\section{Methodology and document structure}

The discretionary M\&S expenditures are linked to six major
subsystems: outer HCal, inner HCal, EMCal, outer tracker, inner
tracker and DAQ/trigger, following the structure established by the
sPHENIX project. For each of the six subsystems, we solicited input
from the collaboration, the project leadership, the three topical
groups and subsystem experts to assemble a comprehensive list of
de-scoping options aimed at reducing individual subsystem costs.  We
also considered as possible options removing entire subsystems from
the experiment. For each identified option, cost savings and the
engineering, design and schedule impact were estimated by project
leadership in consultation with the engineering team and subsystem
experts. The resulting cost, engineering and design impact, at the
level of detail achievable in the time allowed, is described in
Appendix~\ref{cha:engineering}.

The large number of identified options precludes establishing
simulation geometries for all possible combinations of subsystem
configurations and running full \geant simulations for these combined
configurations. Rather, we studied the impact on key physics
performance figures related to three science drivers for each option
individually and for select combinations of options when they were
individually found to have non-negligible impact on the same
performance characteristics. For the various options, the performance
studies were done at different levels of detail, ranging from
generator level studies of loss of statistical precision, to single
particle \geant + reconstruction studies of resolution and bias
effects to full central \auau \hijing \geant + reconstruction
studies. Where applicable, the physics impact of various changes was
also evaluated based on experience with corresponding measurements at
RHIC and the LHC. In particular for the MAPS inner tracking option and
the TPC outer tracker, we consulted with the project managers in the
ALICE upgrade program, Luciano Musa (CERN, ALICE ITS upgrade manager)
and Harald Appelshauser (Frankfurt, TPC project manager) and with
experts from the STAR collaboration (Flemming Videbaek, HFT and iTPC
project manager and Gene van Buren, STAR TPC expert). The resulting
science impact evaluation for all proposed subsystem changes is
described in Appendix~\ref{cha:performance}.

The following sections of the document are organized as follows: We
briefly describe the reference design used to evaluate the relative
performance impact of each subsystem option. Next we provide a concise
summary of the cost, engineering, design and schedule impact and
science impact of each option. This is followed by a rank-ordered
table of options, from least to most undesirable, based on our
evaluation of savings vs.\ engineering and science impact. Following a
summary, we provide an extended discussion of each option's impact in
the Appendix~\ref{cha:engineering} (cost, engineering, and schedule)
and Appendix~\ref{cha:performance} (physics performance). The cost
basis for the de-scoping exercise is seen in the Budget table in
Appendix~\ref{cha:budget}. The numbers in those tables are based on a
bottoms-up estimate for sPHENIX presented at the November 2015 Cost
and Schedule review followed by subsequent cost scrubbing in the
spring of 2016.


