\section{Reference configuration}

All cost changes are evaluated with respect to the detector
configuration discussed in the 2015 Director's cost and schedule
review, which in particular included a TPC outer tracker and a
two-layer inner tracker based on reconfigured VTX pixel
modules. However, based on more detailed simulations of the VTX pixel
performance, including known dead areas, and the operational
experience with the VTX detector in the 2016 RHIC run, this
configuration is not expected to provide acceptable performance for
the sPHENIX science program. This configuration would essentially
preclude the heavy-flavor part of the science program, and not provide
the highly desirable redundancy in tracking performance for the jet
structure and $\Upsilon$ spectroscopy science drivers, in terms of
providing precise track stubs to match to the TPC outer tracker.

The evaluation of the science impact of the subsystem changes is
therefore performed relative to a reference configuration for which
our simulations show excellent physics performance. The reference
configuration uses the HCal, EMCal and TPC subsystems from the cost \&
schedule configuration, but replaces the inner tracker with
a three-layer MAPS based tracker, using a module (``stave'') design
copied from that of the ALICE ITS upgrade inner barrel (IB)
detector. This option was extensively evaluated in a workshop
organized by the LANL group in late March 2016, and attended by ALICE ITS
project management and detector experts (Luciano Musa, CERN and  Leo Greiner, LBNL).  At
the workshop, a detailed cost estimate for this option was prepared,
corresponding to \${\threeLayerMAPS}M FY16 direct M\&S costs for the
IB copy, including engineering costs for integration in the sPHENIX
detector infrastructure.  The full three-layer IB copy therefore
increases the cost of the cost \& schedule configuration by
\${\threeLayerMAPS}M in FY16 M\&S costs, less the \${\noVTX}M that had
been allocated to reconfiguring the VTX pixels. A significant part of
the performance gain associated with the reference configuration could
already be realized with a two-layer MAPS configuration, estimated to be
\${\twoLayerMAPS}M in FY16 M\&S cost.

